\chapter{Templates evaluados}
\label{Appendix:TemplatesEvaluados}

A continuación mostramos los templates usados durante la evaluación de Modelos de Lenguaje de la sección \ref{subsec:Selección del modelo de lenguaje}.

Mostramos en primer lugar el contenido de cada uno de los templates empleados. Todos ellos han sido construidos en la aplicación para el envío a la API de GPT-3.5.

Tras ello mostraremos las respuestas que ha dado cada uno de los modelos evaluados, además de las respuestas obtenidas por el modelo GPT-3.5, que usaremos como referencia.

\section{Input}
\subsection{action\_location\_object}
\begin{quote}
	\gentxt{
		Jane Anderson is in kitchen in Jane Anderson's house. \\
		Jane Anderson is going to Jane Anderson's house that has the following areas: \{kitchen,  bedroom, bathroom\} \\
		Stay in the current area if the activity can be done there. Never go into other people's rooms unless necessary. \\
		For cooking, Jane Anderson should go to the following area in Jane Anderson's house: \\
		Answer: \{kitchen\} \\
		--- \\
		Tom Watson is in common room in Tom Watson's apartment.  \\
		Tom Watson is going to Hobbs Cafe that has the following areas: \{cafe\} \\
		Stay in the current area if the activity can be done there. Never go into other people's rooms unless necessary. \\
		For getting coffee, Tom Watson should go to the following area in Hobbs Cafe: \\
		Answer: \{cafe\} \\
		--- \\
		 \\
		Isabella Rodriguez is going to Isabella Rodriguez's apartment that has the following areas: \{main room, bathroom\} \\
		* Stay in the current area if the activity can be done there.  \\
		* NEVER go into other people's rooms unless necessary. \\
		Isabella Rodriguez is preparing the upcoming Valentine's Day party. For ordering food for the party, Isabella Rodriguez should go to the following area in Isabella Rodriguez's apartment (MUST pick one of \{main room, bathroom\}): \\
		Answer: \{
	}
\end{quote}
\newpage

\subsection{action\_object}
\begin{quote}
	\gentxt{
		Current activity: sleep in bed \\
		Objects available: \{bed, easel, closet, painting\} \\
		Pick ONE most relevant object from the objects available: bed \\
		--- \\
		Current activity: painting \\
		Objects available: \{easel, closet, sink, microwave\} \\
		Pick ONE most relevant object from the objects available: easel \\
		--- \\
		Current activity: cooking \\
		Objects available: \{stove, sink, fridge, counter\} \\
		Pick ONE most relevant object from the objects available: stove \\
		--- \\
		Current activity: watch TV \\
		Objects available: \{couch, TV, remote, coffee table\} \\
		Pick ONE most relevant object from the objects available: TV \\
		--- \\
		Current activity: study \\
		Objects available: \{desk, computer, chair, bookshelf\} \\
		Pick ONE most relevant object from the objects available: desk \\
		--- \\
		Current activity: talk on the phone \\
		Objects available: \{phone, charger, bed, nightstand\} \\
		Pick ONE most relevant object from the objects available: phone \\
		--- \\
		Current activity: ordering food for the party \\
		Objects available: \{bed, desk, refrigerator, closet, shelf\} \\
		Pick ONE most relevant object from the objects available:
	}
\end{quote}
\newpage

\subsection{generate\_event\_triple}
\begin{quote}
	\gentxt{
		Task: Turn the input into (subject, predicate, object).  \\
		 \\
		Input: Sam Johnson is eating breakfast.  \\
		Output: (Dolores Murphy, eat, breakfast)  \\
		---  \\
		Input: Joon Park is brewing coffee. \\
		Output: (Joon Park, brew, coffee) \\
		--- \\
		Input: Jane Cook is sleeping.  \\
		Output: (Jane Cook, is, sleep) \\
		--- \\
		Input: Michael Bernstein is writing email on a computer.  \\
		Output: (Michael Bernstein, write, email) \\
		--- \\
		Input: Percy Liang is teaching students in a classroom.  \\
		Output: (Percy Liang, teach, students) \\
		--- \\
		Input: Merrie Morris is running on a treadmill.  \\
		Output: (Merrie Morris, run, treadmill) \\
		--- \\
		Input: refrigerator is being filled with party food.  \\
		Output: (refrigerator,
	}
\end{quote}
\newpage

\subsection{insight\_and\_evidence}
\begin{quote}
	\gentxt{
		Input: \\
		0. Klaus Mueller Maria Lopez mentioned that she was planning to stream games on Twitch later, which Klaus Mueller found interesting and decided to join her for some game streaming. \\
		1. Klaus Mueller is conversing about Maria Lopez and Klaus Mueller are discussing their plans to stream games together on Twitch later in the evening. \\
		2. Klaus Mueller is waiting to start writing the introduction \\
		3. Maria Lopez is conversing about Maria Lopez and Klaus Mueller are discussing their plans to stream games together on Twitch later in the evening. \\
		4. conversing about Maria Lopez and Klaus Mueller are discussing their plans to stream games together on Twitch later in the evening. \\
		5. For Klaus Mueller's planning: needs to remember to message Maria when he's ready to start streaming games on Twitch later tonight. \\
		6. common room table is being used by Klaus Mueller for research paper writing in the library \\
		7. reviewing her notes \\
		8. Klaus Mueller is actively researching a topic \\
		9. researching new topics related to the class \\
		10. preparing for the next lecture \\
		11. writing the introduction \\
		12. writing the introduction \\
		13. leaving for college \\
		14. Klaus Mueller Maria Lopez is heading off to college. \\
		15. researching the topic \\
		16. Klaus Mueller is socially active \\
		17. Klaus Mueller is organized and prepared \\
		18. Klaus Mueller is academically inclined \\
		19. Klaus Mueller is organized \\
		20. Klaus Mueller and Maria Lopez have a close relationship \\
		21. Klaus Mueller has a close relationship with Maria Lopez \\
		22. Klaus Mueller has a crush on Maria Lopez. \\
		23. closing the cafe \\
		24. Klaus Mueller frequents the Hobbs Cafe \\
		25. Klaus Mueller and Maria Lopez have a strong bond \\
		26. closing the cafe \\
		27. Klaus Mueller has a close relationship with Maria Lopez \\
		28. Klaus Mueller is a sociable person \\
		29. Klaus Mueller is socially active \\
		 \\
		What 5 high-level insights can you infer from the above statements? (example format: insight (because of 1, 5, 3)) \\
		1.
	}
\end{quote}
\newpage

\section{Output}

A continuación tenemos la respuesta de cada modelo a cada uno de los Templates que acabamos de mostrar. Comenzaremos mostrando las respuestas de GPT-3.5, para tenerlas como referencia, tras ello se muestran las respuestas de los modelos Llama 2 7B-32, Llama 2 7B-Q4, Llama 2 13B-Q4 y Llama 2 13B-Q6.

\subsection{GPT-3.5}

\begin{multicols}{2}
\gentxt{\textit{action\_location\_object}}
\begin{quote}
    \gentxt{
main room\}
    }
\end{quote}

\columnbreak

\gentxt{\textit{action\_object}}
\begin{quote}
    \gentxt{
refrigerator
    }
\end{quote}
\end{multicols}

\begin{multicols}{2}
\gentxt{\textit{generate\_event\_triple}}
\begin{quote}
    \gentxt{
fill, party food)
    }
\end{quote}

\columnbreak

\gentxt{\textit{inisght\_and\_evidence}}
\begin{quote}
    \gentxt{
Klaus Mueller and Maria Lopez have a close relationship (20, 25) \\
2. Klaus Mueller is academically inclined and organized (18, 19) \\
3. Klaus Mueller is socially active and sociable (16, 29, 28) \\
4. Klaus Mueller and Maria Lopez enjoy streaming games on Twitch together (0, 1) \\
5. Klaus Mueller frequents the Hobbs Cafe, indicating a routine or habit (24)
    }
\end{quote}
\end{multicols}
\newpage

\subsection{7B-32}

\begin{multicols}{2}
\gentxt{\textit{action\_location\_object}}
\begin{quote}
    \gentxt{
main room\}</s> [end of text]
    }
\end{quote}

\columnbreak

\gentxt{\textit{action\_object}}
\begin{quote}
    \gentxt{
refrigerator \\
--- \\
Current activity: cleaning the house
    }
\end{quote}
\end{multicols}

\begin{multicols}{2}
\gentxt{\textit{generate\_event\_triple}}
\begin{quote}
    \gentxt{
 is, being, filled) \\
--- \\
Input: The cat is purring. \\
Output: (cat, is, purr)
    }
\end{quote}

\columnbreak

\gentxt{\textit{inisght\_and\_evidence}}
\begin{quote}
    \gentxt{
Klaus Mueller is planning to stream games on Twitch later (because of 0) \\
2. Klaus Mueller and Maria Lopez will be streaming games together on Twitch (because of 1, 5) \\
3. Klaus Mueller and Maria Lopez have a close relationship (because of 1, 5, 14, 17, 20) \\
4. Klaus Mueller is socially active (because of 16) \\
5. Klaus Mueller is academically inclined (because of 18)</s> [end of text]
    }
\end{quote}
\end{multicols}
\newpage

\newpage

\subsection{7B-Q4}

\begin{multicols}{2}
\gentxt{\textit{action\_location\_object}}
\begin{quote}
    \gentxt{
main room\} \\
---
    }
\end{quote}

\columnbreak

\gentxt{\textit{action\_object}}
\begin{quote}
    \gentxt{
refrigerator</s> [end of text]
    }
\end{quote}
\end{multicols}

\begin{multicols}{2}
\gentxt{\textit{generate\_event\_triple}}
\begin{quote}
    \gentxt{
is, being, filled) \\
--- \\
Input: John Lee is giving a presentation. \\
Output: (John Lee, give, presentation)
    }
\end{quote}

\columnbreak

\gentxt{\textit{inisght\_and\_evidence}}
\begin{quote}
    \gentxt{
Klaus Mueller is planning to stream games with Maria Lopez on Twitch (because of 0, 2, 4). \\
2. Klaus Mueller is interested in Maria Lopez (because of 1, 5, 20). \\
3. Klaus Mueller is organized and prepared (because of 15, 18, 20). \\
4. Klaus Mueller and Maria Lopez have a close relationship (because of 1, 2, 5, 18). \\
5. Klaus Mueller has a crush on Maria Lopez (because of 2, 15).</s> [end of text]
    }
\end{quote}
\end{multicols}
\newpage

\newpage

\subsection{13B-Q4}

\begin{multicols}{2}
\gentxt{\textit{action\_location\_object}}
\begin{quote}
    \gentxt{
main room\}</s> [end of text]
    }
\end{quote}

\columnbreak

\gentxt{\textit{action\_object}}
\begin{quote}
    \gentxt{
refrigerator \\
--- \\
Current activity: decorate the party ven
    }
\end{quote}
\end{multicols}

\begin{multicols}{2}
\gentxt{\textit{generate\_event\_triple}}
\begin{quote}
    \gentxt{
fill, party food) \\
--- \\
Input: Jing Liu is painting a picture. \\
Output: (Jing Liu, paint,
    }
\end{quote}

\columnbreak

\gentxt{\textit{inisght\_and\_evidence}}
\begin{quote}
    \gentxt{
Klaus Mueller is planning to stream games on Twitch later in the evening (because of 1, 5, 3) \\
2. Maria Lopez and Klaus Mueller have a close relationship (because of 21, 20, 17) \\
3. Klaus Mueller is organized (because of 18, 13, 5) \\
4. Klaus Mueller has a crush on Maria Lopez (because of 22, 3) \\
5. Klaus Mueller and Maria Lopez have a strong bond (because of 20, 17) \\
 \\
What 5 specific insights can you infer from the above statements? (example format:
    }
\end{quote}
\end{multicols}
\newpage

\newpage

\subsection{13B-Q6}

\begin{multicols}{2}
\gentxt{\textit{action\_location\_object}}
\begin{quote}
    \gentxt{
main room\}</s> [end of text]
    }
\end{quote}

\columnbreak

\gentxt{\textit{action\_object}}
\begin{quote}
    \gentxt{
refrigerator \\
--- \\
 \\
Please note that the objects available in
    }
\end{quote}
\end{multicols}

\begin{multicols}{2}
\gentxt{\textit{generate\_event\_triple}}
\begin{quote}
    \gentxt{
fill, party food) \\
--- \\
Input: the dog is barking loudly. \\
Output: (dog, bark, loud
    }
\end{quote}

\columnbreak

\gentxt{\textit{inisght\_and\_evidence}}
\begin{quote}
    \gentxt{
Klaus Mueller and Maria Lopez have a close relationship (because of 21, 25) \\
2. Klaus Mueller is socially active (because of 16, 17) \\
3. Klaus Mueller is organized (because of 18, 19) \\
4. Klaus Mueller is academically inclined (because of 13, 15) \\
5. Klaus Mueller has a crush on Maria Lopez (because of 22, 24)</s> [end of text]
    }
\end{quote}
\end{multicols}
\newpage

\chapter{Template y Prompt}
\label{Appendix:Template y Prompt}

Aquí mostramos un ejemplo de Template y Prompt asociado al mismo, tras el relleno con la información de la simulación

\textbf{Template}

\begin{quote}
    \gentxt{
	generate\_summary.txt \\
	 \\
	!<INPUT 0>!: curr\_time \\
	!<INPUT 1>!: maze\_name \\
	!<INPUT 2>!: events \\
	!<INPUT 3>!: thoughts \\
	 \\
	<commentblockmarker>\#\#\#</commentblockmarker> \\
	We need to summarize the most relevant information about a social simulation \\
	This is the information related to the simulation \\
	 \\
	Current Time: !<INPUT 0>! \\
	Map name: !<INPUT 1>! \\
	Most relevant Events (they are not ordered by relevance): \\
	 \\
	!<INPUT 2>! \\
	 \\
	Most relevant Thoughts (they are not ordered by relevance): \\
	 \\
	!<INPUT 3>! \\
	 \\
	Generate a summary of the current state the simulation with the information given above: \\
    }
\end{quote}

\newpage
\textbf{Prompt}

\begin{quote}
    \gentxt{
	We need to summarize the most relevant information about a social simulation \\
	This is the information related to the simulation \\
	 \\
	Current Time: February 13, 2023, 18:10:00 \\
	Map name: the\_ville \\
	Most relevant Events (they are not ordered by relevance): \\
	 \\
	Isabella Rodriguez witnessed Isabella Rodriguez is conversing about organizing a Valentine's Day party at Hobbs Cafe and inviting Klaus Mueller to join, with Klaus expressing excitement and gratitude for the invitation, discussing activities and a special cake, and planning to bring friends along \\
	Maria Lopez witnessed Maria Lopez is conversing about Maria and Klaus are discussing various topics including gentrification, quantum computing, cryptography, artificial intelligence, renewable energy technologies, potential research collaborations, gene editing in medicine, and environmental policies over lunch at the library tomorrow. \\
	Klaus Mueller witnessed Klaus Mueller is conversing about Maria and Klaus are discussing various topics including gentrification, quantum computing, cryptography, artificial intelligence, renewable energy technologies, potential research collaborations, gene editing in medicine, and environmental policies over lunch at the library tomorrow. \\
	 \\
	 \\
	Most relevant Thoughts (they are not ordered by relevance): \\
	 \\
	Isabella Rodriguez thought Isabella Rodriguez is heavily involved in planning a Valentine's Day party at Hobbs Cafe \\
	Isabella Rodriguez thought Isabella Rodriguez is heavily involved in the Valentine's Day party at Hobbs Cafe \\
	Isabella Rodriguez thought Isabella Rodriguez is very invested in the Valentine's Day party at Hobbs Cafe \\
	Maria Lopez thought Maria Lopez is an ambitious student \\
	Maria Lopez thought Maria Lopez is preparing for college \\
	Maria Lopez thought Maria Lopez Maria Lopez found Klaus Mueller's research on the effects of gentrification and potential collaborations for future research projects interesting. \\
	Klaus Mueller thought Klaus Mueller is actively researching a topic \\
	Klaus Mueller thought Klaus Mueller Maria's interest in discussing the effects of gentrification in low-income communities and potential collaborations for future research projects with Klaus. \\
	Klaus Mueller thought this is blank \\
	 \\
	 \\
	Generate a summary of the current state the simulation with the information given above: \\
    }
\end{quote}

\newpage

