\chapter*{Abstract}

\section*{\tituloPortadaEngVal}

In recent years, numerous applications have emerged that utilize technologies powered by large language models, easing the lives of professionals across various sectors. These models possess a general nature, enabling users to specialize and tailor them to specific cases, generating systems tailored to a particular industry.

While navigating the internet, we encountered the study of \ga \citep{park2023generative}, which captured our attention from the moment we first read it.

This study developed the execution of multi-agent Artificial Intelligence experiments and simulations, with its ultimate goal being to investigate the emergence of social phenomena and relationships between agents. It concluded that agents were indeed capable of retaining memories, interacting with other agents, generating new memories, and planning their next actions.

Upon reading this, we decided to delve deeper into this article, and we discovered that it had captivated the entire Artificial Intelligence research community, as it introduced a novel value and demonstrated that these simulations were coherent. Consequently, several of these research groups embarked on extending the original program, focusing the simulations on performing other types of actions (programming video games autonomously, assigning roles to each agent, for example).

Observing these extensions to the original code, we wondered if we could do something similar ourselves, and develop it as a TFG. After delving into the code and investigating the complete functionality of the application, we had a clear understanding of the use case we wanted to focus on: democratizing this tool and enabling profiles such as psychologists to use it easily.

This became evident because the profiles most likely to be interested in such an application are psychologists and professionals who study social relationships. However, as the project was initially designed, it was quite challenging for a non-tech profile to understand how to use this application. Therefore, with our motivation and main objective clearly defined, we set to work.\\[0.1em]

The code developed during this work is located in https://github.com/NILGroup/TFG-2324-Simulador-MAS-LLM


\section*{Keywords}

\noindent Large language models, emergin behaviors, interaction, interface, technology democratization, intelligent agents



